---
title: "hw2"
author: "cyberatlas"
date: "February 4, 2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

1)
```{r}
faren <- c(-10,15)
print(cel <- ((faren)-32)*(5/9))

```

2)
```{r}
vec200 <- rep(c(1,0), 100)
vec200
```
3)
```{r}
nums <- seq(1,1001)
squardList <- sqrt(nums)
roundSq <- floor(squardList)
setSq <- unique(roundSq)
print(numPerfect <- length(setSq))

```





1)
```{r}
library(ggplot2)
#Loads the data
mpg
#Shows the data
str(mpg)


#Save the mpg table as a dataframe
mpgDF <- data.frame(mpg)
head(mpgDF)

#Sorts the mpg data frame by the hwy value
#Because it sorts in ascending order, we reversed that with a -
sortedList<- mpgDF[order(-mpg$hwy),]
#Makes a data frame with the values at the top of sorted list
top3 <- head(sortedList, 3)
#print the dataframe
print(top3)
```

2)
```{r}
#The reason you need a comma is because it does not know if you are specifying rows or columns
#After the comma, specifies what other columns to return. Not specified = all of them
noRepeats <- mpgDF[mpgDF$class == 'compact',]
print(noRepeats)
#Removes duplicate compact models
noDupes <- unique(noRepeats$model)
#class(noDupes)
#Makes noDupes a data frame
noDupes <- data.frame(noDupes)
str(noDupes)
print(noDupes)
#class(noDupes)
#Variable to store the number of different compact car models 
numCompact <- length(noDupes)
#Prints the number of compact cars on the list
print(numCompact)

```

```{r}
#Grab all of the hwy values by selecting the column in the dataframe
hwy <- data.frame(mpgDF$hwy)
hwy
#Grab all of the cty values by selecting teh column in the dataframe
cty <- data.frame(mpgDF$cty)
cty

#More ggplot stuff 
#http://www.sthda.com/english/wiki/ggplot2-title-main-axis-and-legend-titles
#Uses ggplot2 to make a scatterplot with 
ggplot(mpgDF, aes(x=hwy, y=cty)) +
  geom_point(shape=1) + 
  geom_smooth(method=lm,
              se=FALSE) +
  ggtitle("Hwy by cty")
```


As the hwy increases, the cty is increases more slowly than hwy


```{r}
#Grabs each column and puts them in a dataframe saved in carsByYear
cars1999 <- mpgDF[mpgDF$year == 1999, c('year', 'cty', 'hwy') ]
cars2008 <- mpgDF[mpgDF$year == 2008, c('year', 'cty',"hwy")]

#Prints a boxplot of mpg and year
boxplot(cty~year, data=mpgDF, main="City mpg", xlab = "Year", ylab = "Miles Per Gallon" )
boxplot(hwy~year, data=mpgDF, main="Highway mpg", xlab = "Year", ylab = "Miles Per Gallon")

sprintf("1999 Highway Mean:  %f", mean(cars1999[,"hwy"]))
sprintf("1999 City Mean:  %f", mean(cars1999[,"cty"]))
sprintf("2008 Highway Mean:  %f", mean(cars2008[,"hwy"]))
sprintf("2008 City Mean:  %f", mean(cars2008[,"cty"]))
 

```

Cars in 2008 are not necessarily more efficient than cars in 1999. The means in 1999 show that fuel effiency is slightly higher than in 2008, with the exception of the 2008 highway fuel effiency being slightly larger.
However, in 2008, the percentile ranges are larger. The means in 2008 could be brought down by gas guzzling cars, there also seems to be more higher efficency cars in 2008 than in 1999, with the exception of 2 outliers in Highway Mpg, and 4 in Cty mpg.

